Long groovy title goes here

### 2013-06-24 shanghai.tex
Added proof of Ext^2 triviality and that the resulting diagram is of group schemes

The next step is to show that $\pi: B \to G^0$ extends to a finite etale morphism of group schemes $f: H\to G$, smooth and locally of finite type over $\Fq$, in such a way that $H^0 = B$, $f^0 =\pi$ and $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component groups.
\begin{equation} \label{extension-diagram}
    \xymatrix{
        & A \ar[d] \ar@{=}[r] & A \ar[d] &  \\
        & B \ar[r] \ar[d]_{\pi} & H \ar[r] \ar[d]_{f} & \pi_0(H) \ar[d]_{\pi_0(f)}^{\iso} \\
        & G^0 \ar[r] & G \ar[r] & \pi_0(G).}
\end{equation}
where all rows and columns are exact and all maps are defined over $\Fq$.  We will do so by passing back and forth between group schemes over $\Fq$ and their $\bFq$-points.  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$, correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.  The map $G^0(\bFq) \to G(\bFq)$ induces a map $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$, fitting into the long exact sequence derived from applying $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
$$\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).$$
We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.  
\todo{Stuff missing here.}

>>>>

The next step is to show that $\pi: B \to G^0$ extends to a finite etale morphism of group schemes $f: H\to G$, smooth and locally of finite type over $\Fq$, in such a way that $H^0 = B$, $f^0 =\pi$ and $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component groups.
\begin{equation} \label{extension-diagram}
    \xymatrix{
        & A \ar[d] \ar@{=}[r] & A \ar[d] &  \\
        & B \ar[r] \ar[d]_{\pi} & H \ar[r] \ar[d]_{f} & \pi_0(H) \ar[d]_{\pi_0(f)}^{\iso} \\
        & G^0 \ar[r] & G \ar[r] & \pi_0(G).}
\end{equation}
where all rows and columns are exact and all maps are defined over $\Fq$.  We will do so by passing back and forth between group schemes over $\Fq$ and their $\bFq$-points.  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$, correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.  The map $G^0(\bFq) \to G(\bFq)$ induces a map $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$, fitting into the long exact sequence derived from applying $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
$$\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).$$
We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.

It suffices to show that $\pi_0(G)(\bFq)$ has a two-term resolution by injective $\ZZ[\Gamma]$-modules.  Since the action of $\Gamma$ on $\pi_0(G)(\bFq)$ is continuous, it factor through a finite quotient $\Gamma_m = \Gamma / H_m$.  Any product of Dedekind domains has cohomological dimension $1$ \cite[?]{?}, so $\pi_0(G)(\bFq)$ has a two term resolution by injective $\ZZ[\Gamma_m]$-modules.  Let $I$ be one of these modules: we need to show that $I$ is injective as a $\ZZ[\Gamma]$-module.  Consider the universal diagram for injectivity:
\[
\xymatrix{
& B \\
I & A \ar@{>->}[u] \ar[l]_{a}
}\]
where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.  Since $H_m$ acts trivially on $I$, $I_{H_m}A := \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$  Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
\[
\xymatrix{
& B/I_{H_m}B \ar@{..>}[dl] & B \ar@{->>}[l] \\
I & A/I_{H_m}A \ar@{>->}[u] \ar[l] & A \ar@{>->}[u] \ar@{->>}[l]
}\]
The dotted arrow exists since $I$ is injective as a $\ZZ[\Gamma_m]$-module, and the outer diagram shows that $I$ is injective as a $\ZZ[\Gamma]$-module.

We therefore have the existence of diagram \eqref{extension-diagram} at the level of $\bFq$-points.  This expresses $H(\bFq)$ as a disjoint union of translates of $B(\bFq)$; by transport of structure we may take $H$ to be a group scheme over $\bFq$.  Similarly, the restriction of $f$ to each component of $H$ is a morphism of schemes, and thus $f$ is as well.  Finally, the whole diagram descends to a diagram of $\Fq$-schemes since the $\bFq$-points of the objects come equipped with continuous $\Gamma$-actions, and the morphisms are $\Gamma$-equivariant.
